\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-13 design/search.tex
start intro

\begin{enumerate}
  \item \emph{Year/term}, which is no longer required. It maps to the keywords {\tt \{spring,fall,summer,winter\}} and a four-digit year to specify term and year, and defaults to the current year and term.

>>>>

\begin{enumerate}
  \item \emph{Year/term}, which is no longer a required field. It maps to the keywords {\tt \{spring,fall,summer,winter\}} and a four-digit year to specify term and year, and defaults to the current year and term. Skedge also gets around the fundamental limitation of CDCS of only being able to search one year-term at a time, allowing users to browse \emph{all} of a department's courses at once, for instance.

### 2016-04-13 introduction.tex
start intro

This paper will begin by

@@

CDCS is the University's official tool for

@@

Skedge is a website on which I started rapid development on December 9th 2013, and have been developing it on and off since.

>>>>

In this paper, I am proud to finally introduce the world to \emph{Skedge}, a website I have been developing in various degrees since December 9th, 2013. Skedge began as a weekend side-project for me after spending too much time frustrated with existing tools while trying to find myself a second major to pursue. It wasn't until I briefly presented it at an on-campus RocHack meeting when I realized it had potential to help other students as well, but since, it has always existed in the shadows and in continual ``beta''---unofficial, unsupported and dodging recognition. Until two summers ago, I had never expected it to end up being the subject of my honors senior thesis, so this opportunity represents a rather special privilege for me and, selfishly, an outlet for recognition.

@@

``Course Description / Course Schedule,'' (or \emph{CDCS} for short) is the University's official tool for browsing through the University's current course catalog.

@@

Skedge is a website on which I started rapid development on , and have been developing it on and off since.
